### 2015-03-25 Paper1Editted/paper1Beditted.tex
Paper updates to match rebuttal letter

\subsection*{Intent Extraction: Deducing the Desired Trajectory}
We first demonstrate the \textit{intent extraction} approach in human motor control, but we later show that the process is applicable to any controlled process with an invertible highest order plant term. The process begins by presuming a model of the controller. Here, we choose the well-known motion control structure of Shadmehr and Mussa-Ivaldi\cite{shadmehr1994adaptive} where the feedforward aspect of the controller perfectly predicts the plant and linearizes the system through cancellation. Additionally, linear feedback rejects position and velocity error. This model was chosen to help illuminate the approach, but later we present how to generalize this approach to more complex models without loss of generality. The equation governing the passive planar dynamics (plant) of musculoskeletal structure is of the form,
\begin{equation}
\underbrace{\overbrace{M(q)\ddot{q}}^{\text{Inertia}}+\overbrace{G(q,\dot{q})}^{\text{Coriolis, Centripal}}}_{\text{Plant}}+E=0
\end{equation}
where $M$ is the mass matrix, $q$ is the joint angles, $\dot{q}$ is joint angular velocity, $\ddot{q}$ is joint angular acceleration, $G$ contains both Coriolis and centripetal effects, and $E$ is any externally-applied torque. The motion behavior changes with the addition of feedforward and/or feedback controllers,
\begin{equation}
\underbrace{\overbrace{M(q)\ddot{q}}^{\text{Inertia}}+\overbrace{G(q,\dot{q})}^{\text{Coriolis, Centripal}}}_{\text{Plant}}+E=\underbrace{\overbrace{\hat{M}(q_d)\ddot{q}_d}^{\text{Inertia}}+\overbrace{\hat{G}(q_d,\dot{q}_d)}^{\text{Coriolis, Centripal}}+\hat{E}}_{\text{Feedforward Controller}}+\underbrace{K_p(q_d-q)+K_d(\dot{q}_d-\dot{q})}_{\text{Impendance, Feedback Controller}}
\end{equation}
where terms with hats over them ($\hat{M}$, $\hat{G}$, or $\hat{E}$) indicate that they represent the nervous system's best estimate of the forces and dynamics it will encounter, which is also known as an internal model \cite{shadmehr1994adaptive}. This portion of the system serves as an inverse-dynamics feedforward controller that cancels out the dynamics of the arm in the torque balance. If the nervous system has sufficient experience and is expecting $E$, it is included as part of the internal model, $\hat{E}$, otherwise $\hat{E}$ is set to zero. $K_p$ and $K_d$ are the lumped impedance and feedback terms that employ a moving state equilibrium to accomplish the desired trajectory, $q_d$. This $q_d$ signifies the unknown desired trajectory that we seek to discover.

@@

A key assumption in this study is that the joint impedance (stiffness) is linearly related to torque. While other approaches tend to construct paradigms that indicate or presume that the intention is static in order to derive impedance -- the so called family of system identification applications, this study makes a constrained assumption of stiffness in order to determine intent. In a sense, this approach widens the scope to include movement. Sensitivity analyses showed that approximation of stiffness is the most critical factor to accuracy in estimating intent. While serious trial-to-trial stiffness mis-estimation is unlikely, co-contraction in response to disturbance might plausibly double stiffness mid-reach. Even as the model is insensitive to normal variations, a human can halve or double their stiffness \cite{franklin2007endpoint} significantly reducing determination accuracy. These limitations are readily overcome by performing this sensitivity analysis on each force environment of interest and taking measures to detect co-contraction and hence stiffness alterations. Additionally, real-time determination of intent may allow real-time determination of stiffness.

@@

It is important to mention that it is not necessary for the brain to represent intent explicitly to generate action. It is possible that the nervous system can simply learn the relationship between muscle activations and the accomplishment of goals. For example, one might simply evaluate a motion outcome and adjust descending signals to the muscles. At the same time, one may not deny the fact that there are tasks that require a explicit representation of a trajectory, such as performing a dance, drawing a picture, or conducting an orchestra. For these tasks, intent is likely represented at  some level in the nervous system. Nevertheless, the mechanics of the arm dictate the existence of an equilibrium whether intent is explicitly represented or not. Here our goal was more modest, which was to answer, "where would the arm have gone?"

@@

\begin{figure}
\caption{
{\bf Subjects' disturbed hand trajectories and extraction of intended trajectories from them reveal that both variance and invariance of the motor plan can occur even in response to very large disturbances.} The hand path, in black, deviates from the blue baseline, as a force pulse, gray arrows, is applied. Three of the eight subjects' intent trajectories (orange) did not significantly deviate from undisturbed movement (panel A) as observed by the intent (orange) region (mean $\pm$ 95\% confidence interval on the mean) not departing the undisturbed movement (blue) region. The time at which the hand (black) region departed from undisturbed movement is marked with a green dots. The time of hand departure for the two subjects with similar trajectories is also marked with green dots. Five of the eight subjects' intent trajectories did significantly deviate from undisturbed movement (panel B). The time of intent departure from the undisturbed trajectories is marked with red dots.
}
\label{fig:anecdotes}
\end{figure}

>>>>

\subsection*{Intent Extraction: Deducing the Desired Trajectory}
We first demonstrate the \textit{intent extraction} approach in human motor control, but we later show that the process is applicable to any controlled process with an invertible highest order plant term. The process begins by presuming a model of the controller. Here, we choose the well-known motion control structure of Shadmehr and Mussa-Ivaldi\cite{shadmehr1994adaptive} where the feedforward aspect of the controller perfectly predicts the plant and linearizes the system through cancellation. Additionally, linear feedback rejects position and velocity error. This model was chosen to help illuminate the approach, but later we present how to generalize this approach to more complex models without loss of generality. The equation governing the passive planar dynamics (plant) of musculoskeletal structure is of the form,
\begin{equation}
\underbrace{\overbrace{M(q)\ddot{q}}^{\text{Inertia}}+\overbrace{G(q,\dot{q})}^{\text{Coriolis, Centripal}}}_{\text{Plant}}+E=0
\end{equation}
where $M$ is the mass matrix, $q$ is the joint angles, $\dot{q}$ is joint angular velocity, $\ddot{q}$ is joint angular acceleration, $G$ contains both Coriolis and centripetal effects, and $E$ is any externally-applied torque. The motion behavior changes with the addition of feedforward and/or feedback controllers,
\begin{equation}
\underbrace{\overbrace{M(q)\ddot{q}}^{\text{Inertia}}+\overbrace{G(q,\dot{q})}^{\text{Coriolis, Centripal}}}_{\text{Plant}}+E=\underbrace{\overbrace{\hat{M}(q_d)\ddot{q}_d}^{\text{Inertia}}+\overbrace{\hat{G}(q_d,\dot{q}_d)}^{\text{Coriolis, Centripal}}+\hat{E}}_{\text{Feedforward Controller}}+\underbrace{K_p(q_d-q)+K_d(\dot{q}_d-\dot{q})}_{\text{Impendance, Feedback Controller}}
\end{equation}
where terms with hats over them ($\hat{M}$, $\hat{G}$, or $\hat{E}$) indicate that they represent the nervous system's best estimate of the forces and dynamics it will encounter, which is also known as an internal model \cite{shadmehr1994adaptive}. This portion of the system serves as an inverse-dynamics feedforward controller that cancels out the dynamics of the arm in the torque balance. If the nervous system has sufficient experience and is expecting $E$, it is included as part of the internal model, $\hat{E}$, otherwise $\hat{E}$ is set to zero. $K_p$ and $K_d$ are the lumped impedance and feedback terms that employ a moving state equilibrium to accomplish the desired trajectory, $q_d$. This $q_d$ has a dual meaning in that it signifies both the unknown desired trajectory that we seek to discover and also the moving equilibrium trajectory of the arm.

@@

A key assumption in this study is that the joint impedance (stiffness) is linearly related to torque. While other approaches tend to construct paradigms that indicate or presume that the intention is static in order to derive impedance -- the so called family of system identification applications, this study makes a constrained assumption of stiffness in order to determine intent. In a sense, this approach widens the scope to include movement. Sensitivity analyses showed that approximation of stiffness is the most critical factor to accuracy in estimating intent. While serious trial-to-trial stiffness mis-estimation is unlikely, co-contraction in response to disturbance might plausibly double stiffness mid-reach. Even as the model is insensitive to normal variations, a human can halve or double their stiffness \cite{franklin2007endpoint} significantly reducing determination accuracy. This stiffening may even explain the reported deviation of intent from the baseline trajectories. These limitations are readily overcome by performing this sensitivity analysis on each force environment of interest and taking measures to detect co-contraction and hence stiffness alterations. Additionally, real-time determination of intent may allow real-time determination of stiffness.

@@

It is important to mention that it is not necessary for the brain to represent intent explicitly to generate action. It is possible that the nervous system can simply learn the relationship between muscle activations and the accomplishment of goals. For example, one might simply evaluate a motion outcome and adjust descending signals to the muscles. At the same time, one may not deny the fact that there are tasks that require a explicit representation of a trajectory, such as performing a dance, drawing a picture, or conducting an orchestra. For these tasks, intent is likely represented at  some level in the nervous system. Nevertheless, the mechanics of the arm dictate the existence of an equilibrium whether intent is explicitly represented or not. Here our goal was more modest, which was to answer, ``where would the arm have gone?''

@@

\begin{figure}
\caption{
{\bf Subjects' disturbed hand trajectories and extraction of intended trajectories from them reveal that both variance and invariance of the motor plan can occur even in response to very large disturbances.} The hand path, in black, deviates from the blue baseline, as a force pulse, gray arrows, is applied. Three of the eight subjects' intent trajectories (orange) did not significantly deviate from undisturbed movement (panel A) as observed by the intent (orange) region (mean $\pm$ 95\% confidence interval on the mean) not departing the undisturbed movement (blue) region. The time at which the hand (black) region departed from undisturbed movement is marked with a green dot for each subject. Five of the eight subjects' intent trajectories did significantly deviate from undisturbed movement (panel B). The time of intent departure from the undisturbed trajectories is marked with a red dot for each subject.
}
\label{fig:anecdotes}
\end{figure}
